### 2012-10-29 paper_draft.tex
Added note on insufficiently evaluated PGP-SNPs not being stored
work on tables

\subsection*{Technical implementation of the platform}
The main platform is implemented using the web framework Ruby on Rails 3.0.10. Postgres 9.2 is used as the main database backend for Rails. 
The database stores genotyping results, users' phenotypic information, literature results from Mendeley and the Public Library of Science as well as summaries on SNPs 
which can be found in SNPedia. The literature database of Mendeley is queried using the REST API, which delivers results in JSON. The literature database of 
the Public Library of Science is queried using the respective REST API, which delivers results in an XML-format. Summaries on SNPs are provided by SNPedia, 
through querying the content via the MediaWiki API. The \emph{NHGRI GWAS Catalog} and the \emph{GET Evidence System} provide complete dumps in plain text formats. Those are regularly downloaded and parsed. All databases are queried or parsed using the unique identifier of each SNP as the search term.

@@

\section*{Tables}
\begin{table}
\begin{tabular}{|l|l|l|}
\hline
& Turkey's HSD & \\ \cline{2-3}
& Mean difference & SE \\ \hline
\textbf{Motivation for sharing genotypings in participants} & & \\
\textbf{who are already genotyped} & & \\ \hline 
... curious & 1.159 & 0.193 \\ 
... want to help scientists & 0.465 & 0.128 \\
... for personal benefits & 0.448 & 0.183 \\ \hline
\textbf{Motivation for not sharing in participants} & & \\ 
\textbf{who are not planning to get genotyped} & & \\ \hline
... fear of discrimination & 1.06 & 0.195 \\
... breach of privacy & 0.821 & 0.225 \\
... fear of personalized advertising & 0.848 & 0.208 \\ 
... negative consequences for family members & 0.733 & 0.21 \\ \hline 
\end{tabular}
\caption{Differences in terms of motivation to share genotypings with the public in survey-participants who already received a genotyping compared to participants who are not planning to getting genotyped. }
\label{tab:motivations1}
\end{table}

\begin{table}
\begin{tabular}{|l|l|l|}
\hline
& Turkey's HSD & \\ \cline{2-3}
& Mean difference & SE \\ \hline
\textbf{Motivation for sharing genotypings in participants} & & \\
\textbf{who would share with their DTC provider} & & \\ \hline
... curiosity & 1.99 & 0.321 \\
... want to help science & 1.57 & 0.199 \\
... for personal benefits & 0.951 & 0.308 \\ \hline
\textbf{Motivation for sharing genotypings in participants} & & \\
\textbf{who would not share with their DTC provider} & & \\ \hline
... fear of discrimination & 1.52 & 0.322 \\
... fear of consequences for family members & 1.146 & 0.32 \\
... fear of personalized advertising & 1.112 & 0.357 \\ \hline
\end{tabular}
\caption{Differences in terms of motivations to share genotyping-data, comparison between participants who would share their genotyping data with their DTC provider with participants who would not share their data with their DTC provider.}
\label{tab:motivations2}
\end{table}
%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}

>>>>

\subsection*{Technical implementation of the platform}
The main platform is implemented using the web framework Ruby on Rails 3.0.10. Postgres 9.2 is used as the main database backend for Rails. 
The database stores genotyping results, users' phenotypic information, literature results from Mendeley and the Public Library of Science as well as summaries on SNPs 
which can be found in SNPedia. The literature database of Mendeley is queried using the REST API, which delivers results in JSON. The literature database of 
the Public Library of Science is queried using the respective REST API, which delivers results in an XML-format. Summaries on SNPs are provided by SNPedia, 
through querying the content via the MediaWiki API. The \emph{NHGRI GWAS Catalog} and the \emph{GET Evidence System} provide complete dumps in plain text formats. Those are regularly downloaded and parsed. SNPs that are described as 'Insufficiently evaluated' in the \emph{GET Evidence System} are not stored. All databases are queried or parsed using the unique identifier of each SNP as the search term.

@@

\section*{Tables}
\begin{table}
\begin{tabular}{|l|l|l|l|l|}
\hline
& Mean & Mean & Tukey's HSD & \\ 
& \emph{Genotyped} & \emph{Not Genotyped} & Mean difference & SE \\ \hline
\textbf{Motivation for sharing genotypings in participants} & & & & \\
\textbf{who are already genotyped} & & & & \\ \hline 
... curious & 3.82 & 2.66 & 1.159 & 0.193 \\ 
... want to help scientists & 4.64 & 4.18  & 0.465 & 0.128 \\
... for personal benefits & 3.77 & 3.32  & 0.448 & 0.183 \\ \hline
\textbf{Motivation for not sharing in participants} & & & & \\ 
\textbf{who are not planning to get genotyped} & & & & \\ \hline
... fear of discrimination & 3.09 & 4.15  & 1.06 & 0.195 \\
... breach of privacy & 3.01 & 3.68  & 0.821 & 0.225 \\
... fear of personalized advertising & 3.03 & 3.88  & 0.848 & 0.208 \\ 
... negative consequences for family members & 2.93 & 3.57  & 0.733 & 0.21 \\ \hline 
\end{tabular}
\caption{Differences in terms of motivation to share genotypings with the public in survey-participants who already received a genotyping compared to participants who are not planning to getting genotyped. }
\label{tab:motivations1}
\end{table}

\begin{table}
\begin{tabular}{|l|l|l|l|l|}
\hline
& Mean & Mean & Tukey's HSD & \\ 
& \emph{Sharing} & \emph{Not Sharing} & Mean difference & SE \\ \hline
\textbf{Motivation for sharing genotypings in participants} & & & & \\
\textbf{who would share} & & & & \\ \hline
... curiosity & 3.86 & 1.87 & 1.99 & 0.321 \\
... want to help science & 4.44 & 3.19 & 1.57 & 0.199 \\
... for personal benefits & 3.68 & 2.73 & 0.951 & 0.308 \\ \hline
\textbf{Motivation for sharing genotypings in participants} & & & & \\
\textbf{who would not share} & & & & \\ \hline
... fear of discrimination & 3.21 & 4.73 & 1.52 & 0.322 \\
... fear of consequences for family members & 2.79 & 3.93 & 1.146 & 0.32 \\
... fear of personalized advertising & 3.17 & 4.29 & 1.112 & 0.357 \\ \hline
\end{tabular}
\caption{Differences in terms of motivations to share genotyping-data, comparison between participants who would share their genotyping data with participants who would not share their data.}
\label{tab:motivations2}
\end{table}
%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}
